% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faPuzzlePiece}

\begin{projects}
	\project
	{Employee Attrition Prediction}{2020}
	{\github{Ankit512/Employee-Attrition-Prediction}}
	{Developed a model that could predict which employees are more likely to quit their job. This is a fictional dataset created by an IBM data scientist and it's available on Kaggle. The project involves Data Visualization, Data Mining, Data Cleaning and Data Modeling techniques and implements ML algorithms for model training and testing.}
	{Python 3, Pandas, NumPy, scikit-learn, Tensorflow, Matplotlib, Seaborn, Jupyter Notebook}
				
	\project
	{Service request data analysis of New York City 311 calls}{2020}
	{\github{Ankit512/Service-request-data-analysis-of-New-York-City-311-calls}}
	{This project studies and visualizes the 311 Service Requests for all non-emergency requests from the city, including but not limited to noise complaints, air quality issues and reports of unsanitary conditions etc. The 311 calls in New York City (NYC) are publicly available. 311 service request dataset is available at NYC OpenData. Analysis of 311 calls can be of great use for a wide variety of purposes, ranging from a rich understanding of the status of a city to the effectiveness of the government services in addressing such calls. }
	{Python 3, Pandas, Matplotlib, Seaborn, Jupyter Notebook}
	
	\project
	{FPS Minigame}{2020}
	{\github{Ankit512/FPS-Minigame}}
	{This is an FPS game built in Unity 3D. The successful design of the FPS Minigame with the correct direction, attractive graphics, and models will give the best experience to play the game. The main design element of this type of game is combat and action-centered. This game also comes under role player category too because the player has to play with the protagonist's point of view. The game consists of two levels.}
	{Unity 3D, C\#, Unity Standard Assets}
	
	\project
	{Dining Philosophers GUI}{2020}
	{\github{Ankit512/Dining-Philosophers-GUI}}
	{A java based approach to the solution of the famous Dining Philosophers problem which illustrates synchronization issues and techniques for resolving them.}
	{Java, NetBeans IDE}
	
	\project
	{Super Sparty Bros.}{2019}
	{\github{Ankit512/Super-Sparty-Bros}}
	{A 2D platformer game that mimics Mario built in Unity3D. Players can experience the nostalgia of the 16-bit gaming popular during the late 90's.This game consists of two levels. This game also comes under role player category too because the player has to play with the protagonist's point of view.}
	{Unity 3D, C\#, Autodesk SketchBook}
	

\end{projects}